\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-02-01 src/010chap1.tex
- completed chapter 1. am. not. working. on. this. anymore. -- binary matrix example has been transposed to show cop on rows. - added section with illustration problem worked out in chapter 3. this shit is done.

\tnote[dire]{
\section[Basic preliminaries]{Basic preliminaries} 
\label{sec:basicprelim}

If $n$ is a positive integer, $[n]$ denotes the set $\{1,2,... n\}$.

\begin{definition}[Binary matrix]
  \label{def:binmatrix}
  Let $M$ be an $n \times m$ matrix. $m_{i,j}$ denotes its $(i,j)$th
  element, i.e. element at $i$th row and $j$th column. $M$ is a \textbf{binary
  matrix} if each of its element is 0 or \un.  In other words, for all
  $i \in [n]$ and $j \in [m]$, $m_{i,j} \in \{0, \un\}$
\end{definition}

\begin{definition}[Permutation]
  A \textbf{permutation} $\lambda$ of a set $X = \{x_1, x_2, \ldots
  x_n\}$ is a bijection $\lambda: X \rightarrow X$.  For simplicity,
  $\lambda$ may be written as a sequence $x_{i_1}x_{i_2}\ldots x_{i_n}$,
  where $i_j \in [n]$ to mean that $\lambda(x_j)= x_{i_j}$.
  This document uses both notations as convenient in context.
\end{definition}

\begin{definition}[\Cop]
  \label{def:copmatrix}
  Let $M$ be a binary matrix.
  \begin{itemize}
  \item \textbf{\Cop}
  \item \textbf{Strong \cop}
  \item \textbf{\Cop order} or \cop permutation
  \end{itemize}
\end{definition}

@@

\begin{definition}[\Crop]
  \label{def:cropmatrix}
\end{definition}

\begin{definition}[Set system]
  \label{def:setsystem}

  Let $U$ be a universe with $|U| = n$.  
  \begin{itemize}
  \item The set $\F \subseteq (2^{U} \setminus \emptyset)$ is called a
    \textbf{set system} with universe $U$.
  \item Two sets $S, S' \in \cF$ are said to \textbf{overlap}, denoted
    by $S \overlap S'$, if they have a non-empty intersection and
    neither is contained in the other.
    \[S \overlap S' \text{ \iff\ } S \cap S' \ne \emptyset, S
    \nsubseteq S', S' \nsubseteq S\]
  \end{itemize}
\end{definition}

\begin{definition}[Partial order]
  \label{def:poset}    
  Let $A$ be a set and $R$ be a binary relation $R \subseteq A \times
  A$.

  \textbf{poset}

  Let $X$ be a partially ordered set with $\preccurlyeq$ being the
  partial order on $X$.

  \begin{itemize}
  \item \textbf{hasse diagram}
  \item \textbf{maximal upper bound}  $X_m \in X$ is a \textbf{maximal upper bound} of $X$
  if $\nexists X_q \in X$ such that $X_m \preccurlyeq X_q$.  A maximal
  upper bound on $X$ is denoted by $mub(X)$.

  \item A set of sets form a \textbf{single
      inclusion chain} when the Hasse diagram of their subset relation
    forms a single chain.
  \end{itemize}
\end{definition}

\begin{definition}[Graph, Tree]
  \label{def:graphtree}  
  \tnote[dire]{take from doms}
\end{definition}

When refering to a tree as $T$ it could be a reference to the tree
itself, or the vertices of the tree. This will be clear from the
context.

@@

\begin{definition}[Interval graph, Path graph]
  \label{def:pathgraph}

  \begin{itemize}
  \item A graph $G$ is an \textbf{interval graph} if there a set of intervals
    $\cI$ \stt $G$ is isomorphic to the intersection graph of
    $\cI$. \[G \cong \bI(\cI)\]
  \item A graph $G$ is a \textbf{path graph} if there exists a tree $T$ and a
    set of paths from $T$, $\cP$ \stt $G$ is isomorphic to the
    intersection graph of $\cP$. \[G \cong \bI(\cP)\]
  \end{itemize}
\end{definition}
Moreover, a \textbf{chordal graph} is characterized as an intersection
graph of subtrees of a tree.

\begin{definition}[Maximal clique]
  \label{def:maxclique}    
\end{definition}
}

>>>>

\section[Basic preliminaries]{Basic preliminaries} 
\label{sec:basicprelim}

Here we see some basic definitions and conventions necessary for the contents
of this thesis.

\subsection{Matrices}
If $n$ is a positive integer, $[n]$ denotes the set $\{1,2,... n\}$.

\begin{definition}[Binary matrix]
  \label{def:binmatrix}
  Let $M$ be an $n \times m$ matrix. $m_{i,j}$ denotes its $(i,j)$th
  element, i.e. element at $i$th row and $j$th column. $M$ is a
  \textbf{binary matrix} if each of its element is 0 or \un; for all
  $i \in [n]$ and $j \in [m]$, $m_{i,j} \in \{0, \un\}$
\end{definition}

\begin{definition}[Permutation]
  A \textbf{permutation} $\lambda$ of a set $X = \{x_1, x_2, \ldots
  x_n\}$ is a bijection $\lambda: X \rightarrow X$.  $\lambda$ may be
  written as a sequence $x_{i_1}x_{i_2}\ldots x_{i_n}$, where $i_j \in
  [n]$ to mean that $\lambda(x_j)= x_{i_j}$.  This document uses both
  notations as convenient in context.
\end{definition}

The idea of \cop of binary matrices was mentioned a few times in
earlier sections. Now we will see the formal definition of \COP in
Definition~\ref{{def:copmatrix}}.

\begin{definition}[\Cop (on columns)]
  \label{def:copmatrix}
  Let $M$ be a binary matrix.
  \begin{enumerate}
  \hangindent \defindent
  \item A \textbf{block of \un s (block of 0s)} in a column of $M$ is a maximal set of
    consecutive \un-entries (0-entries) in this column.
  \item $M$ has the \textbf{strong \cop
      (strong \COP)} if in every column the \un s appear consecutively,
    \ie if every column contains at most one block of \un s.
  \item $M$ has the \textbf{\cop} if its rows can be
    permuted in such a way that the resulting matrix has the strong \COP.
  \item If an ordering for the rows of $M$ gives the strong \COP, it
    is called a \textbf{\COP order} or \textbf{\COP permutation}.
  \end{enumerate}
\end{definition}

When the roles of rows and columns are exchanged in
Definition~\ref{def:copmatrix}, it defines \COP on rows. Both
are equivalent properties (for the purposes of this thesis) and both
conventions are seen the literature.
Figure~\ref{fig:cop-matrix} gives an example of \COP on columns.

@@

A less restrictive property of binary matrices that is a
generalization of the \COP is \crop (\CROP). The matrix can be
visualized to be wrapped around a horizontal cylinder and demands that
after some row permutations, if required, in every column the \un s
appear consecutively on the cylinder -- note that this implies the 0s
also appear consecutively.

\begin{definition}[\Crop (on columns)]
  \label{def:cropmatrix}
  Let $M$ be a binary matrix.
  \begin{enumerate}
  \hangindent \defindent
  \item $M$ has the \textbf{strong \crop (strong \CROP)} if in every
    column the \un s appear consecutively or the 0s appear
    consecutively or both.
  \item $M$ has the \textbf{\crop (\CROP)} if its rows can be permuted
    in such a way that the resulting matrix has the strong \CROP.
  \item If an ordering for the rows of $M$ gives the strong \CROP,
    then it is called the \textbf{\CROP ordering} or \textbf{\CROP
      permutation}.
  \end{enumerate}
\end{definition}

\subsection{Sets}

\begin{definition}[Set system]
  \label{def:setsystem}
  Let $U$ be a universe with $|U| = n$.  
  \begin{enumerate}
  \hangindent \defindent
  \item The set $\F \subseteq (2^{U} \setminus \emptyset)$ is called a
    \textbf{set system} with universe $U$.
  \item Two sets $S, S' \in \cF$ are said to \textbf{overlap}, denoted
    by $S \overlap S'$, if they have a non-empty intersection and
    neither is contained in the other.
    \[S \overlap S' \text{ \iff\ } S \cap S' \ne \emptyset, S
    \nsubseteq S', S' \nsubseteq S\]
  \end{enumerate}
\end{definition}

\begin{definition}
  \label{def:poset}    
%   Let $A$ be a set and $R$ be a binary relation $R \subseteq A \times
%   A$.

%   \textbf{poset}
  Let $X$ be a partially ordered set with $\preccurlyeq$ being the
  partial order on $X$.

  \begin{enumerate}
  \hangindent \defindent
%  \item \textbf{hasse diagram}
  \item An element $X_m \in X$ is a
    \textbf{maximal upper bound} of $X$ if $\nexists X_q \in X$ such
    that $X_m \preccurlyeq X_q$.  A maximal upper bound on $X$ is
    denoted by $mub(X)$.

  \item A set of sets form a \textbf{single
      inclusion chain} when the Hasse diagram of their subset relation
    forms a single chain.
  \end{enumerate}
\end{definition}

\subsection{Graphs}

\begin{definition}[Graph, Tree, Path]
  \label{def:graphtree}
  \begin{enumerate}
    \hangindent \defindent
  \item An \textbf{(undirected) graph} is $G = (V,E)$ is \stt $V$ is a
    finite set and $E$ is a set of ordered pairs, $E \subseteq V
    \times V$. An element in $V$ is called a \textbf{vertex
      (\emph{pl.} vertices)} and an element from $E$ is called an
    \textbf{edge}. $V$ and $E$ may be written as $V(G)$ and $E(G)$
    respectively. If $u,v \in V$ and $(u,v) \in E$ then $v$ is said to
    be \textbf{adjacent} to $u$ and vice versa. A \textbf{subgraph} of
    $G$ is a graph $G' = (V',E')$ \stt $V' \subseteq V$ and $E'
    \subseteq E$.

  \item A \textbf{path} is a graph $P = (V,E)$ with vertex set $V =
    \{v_1,\ldots,v_n\}$ and edge set $E= \{ (v_1,v_2),(v_2,v_3),
    \ldots,(v_{n-2},v_{n-1}),(v_{n-1},v_{n})\}$. The vertices $v_1,
    v_n$ are called the \textbf{endpoints} of $P$. The graph $P$ is
    called a \textbf{cycle} if it has an additional edge $(v_n,v_1)$.

  \item A \textbf{tree} is a graph $T$ that has no subgraph that is a
    cycle.
  \end{enumerate}
\end{definition}

% When refering to a tree as $T$ it could be a reference to the tree
% itself, or the vertices of the tree. This will be clear from the
% context.

@@

\begin{definition}[Interval graph, Path graph]
  \label{def:pathgraph}
  Let $G$ be a graph.
  \begin{enumerate}
  \hangindent \defindent
  \item $G$ is an \textbf{interval graph} if there a set of intervals
    $\cI$ \stt $G$ is isomorphic to the intersection graph of
    $\cI$. \[G \cong \bI(\cI)\]
  \item $G$ is a \textbf{path graph} if there exists a tree $T$ and a
    set of paths from $T$, $\cP$ \stt $G$ is isomorphic to the
    intersection graph of $\cP$. \[G \cong \bI(\cP)\]
  \item $G$ is a \textbf{chordal graph} if it has no induced cycle of
    length greater than 3. Moreover, a \textbf{chordal graph} is
    characterized as an intersection graph of subtrees of a tree.
  \end{enumerate}
\end{definition}

### 2012-02-01 src/030chap3.tex
- completed chapter 1. am. not. working. on. this. anymore. -- binary matrix example has been transposed to show cop on rows. - added section with illustration problem worked out in chapter 3. this shit is done.

\tnote[dire]{ inthis section we run through the algorithm in the
  problem introduced in chapter 1.}

\section[Special target trees]{ Computing feasible TPL with special target trees}
\label{sec:spltargettree}

>>>>

In this section we run through the filtering and tree pruning
algorithm seen in Section~\ref{sec:feasible} on an example. The
example problem is the \illustrationproblem posed in
Section~\ref{sec:problem}.  % Chapter~\ref{ch:intro}
The solution is depicted in Figure~\ref{fig:solpartI},
Figure~\ref{fig:solpartIII}, Figure~\ref{fig:solpartIVa},
Figure~\ref{fig:solpartIVb}, Figure~\ref{fig:solpartVI},
Figure~\ref{fig:solpartVII}, Figure~\ref{fig:solpartVIII} and the
figures along with their captions are self-explanatory.

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    $T:$ \infiniteloopI & $\cF:$ \studygroupsI
  \end{tabular}

  \caption[\figtabsize Problem solution part 1]{\figtabsize The
    problem is shown again here using the input described in
    Section~\ref{sec:problem}. The target tree is $T$ with vertex set
    $\{1,2,\ldots,11\}$ on the left hand side along with the path
    system (hypergraph) -- $\{7,2,6,5\}, \{8,2,4\}, \{10,6,5,3\},
    \{9,1,5,3,11\}$. The hypergraph is $\cF$ with hyperedges $\{\xPa,
    \xPi, \xVi, \xCh\}, \{\xSn, \xWo, \xPi\}, \{\xCh, \xFr, \xVi,
    \xLi\}, \{\xLu, \xSa, \xSc, \xCh, \xFr\}$ shown in the right hand
    side. In subsequent illustrations, the gray boxes which contain
    the elements of universe $U$, will be assigned to nodes and
    removed from the right hand side figure and placed next to the
    vertex of $T$ in the left hand side figure.  The path labeling is
    implicitly given by the color-coded Venn diagrams (the order of
    listing of the hyperedges in this caption is also done respective
    to the input path labeling).}
  \label{fig:solpartI}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIII 
    & 
    \studygroupsIII 
    &
    \studygroupsIIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 2]{\figtabsize It can be observed in
    Figure~\ref{fig:solpartI}, that none of the leaves are shared by
    more than one path. Hence, \filteri does not alter the
    hypergraphs. \filterii finds the leaf assignments as shown --
    elements \xPa, \xSn, \xLu, \xSc, \xLi, \xWo are assigned to
    vertices 7, 8, 9, 11, 10, 4 respectively. Computation of these
    leaf labels are deterministic except for $\xLu, \xSc$ where the
    algorithm arbritarily choses them from $X = \{\xLu, \xSa, \xSc\}$
    and for $\xSn, \xWo$ arbitrarily choses from $X = \{\xSn,
    \xWo\}$. Here we show only one such choice and clearly one could
    have chosen another leaf label (\eg $\xSa$ on 9 or $\xWo$ on 8) to
    get a different feasible hypergraph isomorphism.  After
    this, the leaves of $T$ are pruned and the hypergraph updated
    accordingly by \algoiii subroutine -- the pruned leaves are shown
    with dotted edges and the corresponding Venn diagrams show the
    updated hypergraphs. $\phi_0$ is this leaf assignment and the
    algorithm proceeds to solve the subproblem with the new
    hypergraphs and path labeling which is: $\{2,6,5\}, \{2\},
    \{6,5,3\}, \{1,5,3\}$ labeled with $\{\xPi, \xVi, \xCh\},
    \{\xPi\}, \{\xCh, \xFr, \xVi\}, \{\xSa, \xCh, \xFr\}$
    respectively.}
  \label{fig:solpartIII}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIVa
    & 
    \studygroupsIVa
  \end{tabular}
  \caption[\figtabsize Problem solution part 3]{\figtabsize In the subproblem shown in
    Figure~\ref{fig:solpartIII}, it can be noted that there are two
    leaves which are shared by more than one paths -- 2 and 3. Hence
    \filteri filters this out one by one. Here we show the handling of
    leaf 2 which was shared by paths $\{2,6,5\}$ ($=P_1$, say) and
    $\{2\}$($=P_2$, say). \filteri removes $P_1$ and adds
    $\{6,5\}$. Note that only one set is added and removed since $P_2
    \subset P_1$. Accordingly, \filteri alters the hypergraph on the
  right hand side by removing and adding $\{\xPi, \xVi, \xCh\}$ and $\{\xVi, \xCh\}$ respectively.}
  \label{fig:solpartIVa}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIVb
    & 
    \studygroupsIVb
  \end{tabular}
  \caption[\figtabsize Problem solution part 4]{\figtabsize After handling leaf 2, \filteri proceeds to
    handle leaf 3 which is shared by paths $\{1,5,3\}$ and
    $\{6,5,3\}$. \filteri removes these two paths and adds their
    intersection and set differences -- $\{5,3\}$, $\{1\}$ and
    $\{6\}$. Correspondingly, hyperedges $\{\xSa, \xCh, \xFr\}$ and $\{\xVi,
    \xCh, \xFr\}$ are removed and new hyperedges $\{\xCh, \xFr\}$, $\{\xSa\}$
    and $\{\xVi\}$ respectively are added. There are no more leaves
    shared and the algorithm proceeds to \filterii.}
  \label{fig:solpartIVb}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopVI
    & 
    \studygroupsVI
    &
    \studygroupsVItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 5]{\figtabsize \filterii computes the leaf assignment $\phi_1$ -- $\xPi,
    \xSa, \xFr$ on 2,1,3 respectively. These assignments are
    deterministic since $X$ consisted of only single elements for each
  of these leaves. After this the rest of the labeling is fairly
  obvious but we present it in Figure~\ref{fig:solpartVII} for the
  sake of completeness.}
  \label{fig:solpartVI}  
\end{figure}
\clearpage

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}

    \infiniteloopVII 
    &
    &
    \studygroupsVIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 6]{\figtabsize The last part of the isomorphism is computed as
  the leaf label $\phi_2$ which maps $\xCh, \xVi$ to 5, 6
  respectively. Figure~\ref{fig:solpartVIII} shows the final
  feasibility isomorphism which is the union of all the leaf labels.}
  \label{fig:solpartVII}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopVIII
    &
    &
    \studygroupsVIIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 7]{\figtabsize The solution to the problem presented in
    Figure~\ref{fig:solpartI}. The feasibility hypergraph isomorphism
    $\phi$ is computed as the union of the leaf labels
    $\phi_0,\phi_1,\phi_2$. One can easily verify that this
    isomorphism does indeed induce the path labeling given in the
    original input.}
  \label{fig:solpartVIII}
\end{figure}

%\clearpage
\section[Special target trees]{ Computing feasible TPL with special target trees}
\label{sec:spltargettree}

### 2012-02-01 src/thesis.tex
- a whole bunch of cleanups. see diff. - removed problem defs from chap 1. they were duplicates from chap 3. - CODED FIGURES IN TIKZ. forbidden subgraphs, graphmatrix example graphs. - BEGAN CHAPTER 3 EDITS.
Formatting/layout changes
-------

- Added FrenchLayout to make lists denser
- Added hanging indent for Definitions
- Compressed theorem env's above below spaces
- Creaded env for problem definition minipages.
- moved all clearpage/page counter and other prechapter settings to the chapter tex files.
- Fixed the page number bug in draft printout. removed \fancyhf{} to avoid resetting page n

%% Drafting libraries %%
%
\usepackage[color,notcite,notref]{showkeys}   % To show keys used - useful in
                               % drafts. 
                               % Options: color, notref, notcite,
                               % draft(default), final

\newcommand{\xclearpage}{\cleardoublepage} % cleardoublepage for
                                % twoside. keep empty for one side.
\usepackage[inline] 
%\usepackage[margins] 
%\usepackage[finalnew]
         {../lib/trackchanges} % For tracking changes.
                               % :Package options:
                               % [finalold]
                               %   Ignore all of the edits. 
                               %   The document will look as if
                               %   the edits had not been added. 
                               % [finalnew]
                               %   Accept all of the edits. 
                               %   Notes will not be shown in the
                               %   final output. 
                               % [footnotes]
                               %   Added text will be shown
                               %   inline. Removed text and notes
                               %   will be shown as footnotes.  
                               %   This is the default option.
                               % [margins]
                               %   Added text will be shown
                               %   inline. Removed text and notes
                               %   will be shown in the
                               %   margin. Margin notes will be
                               %   aligned with the edits when
                               %   possible. 
                               % [inline]
                               %   All changes and notes will be
                               %   shown inline.

@@

% \usepackage{comment}         % DEBUG ONLY
%\includeonly{010chap1}         % DEBUG ONLY 
%\includeonly{020chap2}         % DEBUG ONLY 
%\includeonly{030chap3,050appa}         % DEBUG ONLY 
%\includeonly{0031ded}         % DEBUG ONLY

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
%

\xclearpage% \cleardoublepage
\setcounter{page}{1}
\include{001certificate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
%
\xclearpage
\include{002ack}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedication?
%
\xclearpage
\include{0031ded}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%
\xclearpage
\include{003abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.
%
\begin{singlespace}
  \xclearpage
  \tableofcontents
  \thispagestyle{empty}
  \xclearpage
  \listoftables %\addcontentsline{toc}{chapter}{LIST OF TABLES}
  \xclearpage
  \listoffigures %\addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
%
\xclearpage
\include{004abbrv}

@@

\xclearpage
\pagestyle{fancy}%headings}   % For running headers.
\fancyhf{}%            % Clears headers
\fancyhead[LE,RO]{\scriptsize \slshape \rightmark} %{\slshape \rightmark}
\fancyhead[LO,RE]{\scriptsize \slshape \leftmark} %{\slshape \leftmark}
\pagenumbering{arabic} % The main text will follow from this point so
                       %  set the page numbering to arabic from here on.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main body Chapters
%
\include{010chap1}
% turning counter reset. perhaps universal endnote counter is good?
% being schizo about it now. DECIDE! ENDNOTEMARKS DEPEND ON IT.
%\setcounter{endnote}{0} % need to empty the file too. how?! -
                        % FIXED. turns out, just having notes is
                        % enough. or maybe it was fluke.
\xclearpage
\include{020chap2}
\xclearpage
\include{030chap3}
\xclearpage
\include{040chap4}

@@

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.
%
\begin{singlespace}
%  \addcontentsline{toc}{chapter}{REFERENCES }

  \tnote[minor]{(i)make names
    in bib file uniform style w.r.t. firstname/initials (ii) have back
  refs - i.e. pages that cite the item.}
  {\footnotesize%
    \bibliographystyle{alpha}%
    \bibliography{../lib/cop-variants__thesis} %
  }
\end{singlespace}

>>>>

%% Drafting libraries %%
%
\usepackage[color,notcite,notref,final]{showkeys}   % To show keys used - useful in
                               % drafts. 
                               % Options: color, notref, notcite,
                               % draft(default), final

\newcommand{\xclearpage}{\cleardoublepage} % cleardoublepage for
                                % twoside. keep empty for one side.
%\usepackage[inline] 
%\usepackage[margins] 
\usepackage[finalnew]
         {../lib/trackchanges} % For tracking changes.
                               % :Package options:
                               % [finalold]
                               %   Ignore all of the edits. 
                               %   The document will look as if
                               %   the edits had not been added. 
                               % [finalnew]
                               %   Accept all of the edits. 
                               %   Notes will not be shown in the
                               %   final output. 
                               % [footnotes]
                               %   Added text will be shown
                               %   inline. Removed text and notes
                               %   will be shown as footnotes.  
                               %   This is the default option.
                               % [margins]
                               %   Added text will be shown
                               %   inline. Removed text and notes
                               %   will be shown in the
                               %   margin. Margin notes will be
                               %   aligned with the edits when
                               %   possible. 
                               % [inline]
                               %   All changes and notes will be
                               %   shown inline.

@@

% \usepackage{comment}         % DEBUG ONLY
\includeonly{010chap1}         % DEBUG ONLY 
%\includeonly{020chap2}         % DEBUG ONLY 
%\includeonly{010chap1, 020chap2}         % DEBUG ONLY 
%\includeonly{030chap3,050appa}         % DEBUG ONLY 
%\includeonly{0031ded}         % DEBUG ONLY
%\includeonly{020chap2}         % DEBUG ONLY 
%\includeonly{_tempscrap}         % DEBUG ONLY 
%\figforbiddensubgraphs

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
%
\include{001certificate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
%
\include{002ack}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedication?
%
\include{0031ded}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%
\include{003abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.
%
\begin{singlespace}
  \xclearpage
  \tableofcontents
  \thispagestyle{empty}
  \xclearpage
  \listoftables 
  \xclearpage
  \listoffigures
\end{singlespace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
%
\include{004abbrv}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main body Chapters
%
\xclearpage
\pagestyle{fancy}%headings}   % For running headers.
%\fancyhf{}%            % Clears headers -- ALSO REMOVES PAGE
                        % NUMBERS. IF USED, PUT PG# IN FOOTER.
\fancyhead[LE,RO]{\scriptsize \slshape \rightmark} %{\slshape \rightmark}
\fancyhead[LO,RE]{\scriptsize \slshape \leftmark} %{\slshape \leftmark}
\pagenumbering{arabic} % The main text will follow from this point so
                       %  set the page numbering to arabic from here on.

\include{010chap1}

\include{020chap2}

\include{030chap3}

\include{040chap4}

@@

\include{_tempscrap}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.
%
\include{biblio}
